---
title: "Wordscores mit `quanteda` (offizielles Quanteda-Tutorial in Englisch)" 
author: "Philipp Meyer, Institut für Politikwissenschaft"
date: "09.06.2021, Supervised (text) classification, Seminar: Quantitative Textanalyse"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
editor_options: 
  chunk_output_type: console
---

# 1. Einleitung

Dieses Tutorial soll euch die Wordscores-Methode näherbringen. Hierbei handelt es sich, ähnlich wie bei Naïve Bayse um eine supervised classification. Wordscores wurde maßgeblich von Ken Benoit entwickelt und in `quanteda` implementiert. Aus diesem Grund werde ich hier das offizielle Tutorial von `quanteda` bereitstellen. Die Originalquelle findet ihr [hier](https://tutorials.quanteda.io/machine-learning/wordscores/).

# 2. Offizielles WORDSCORES-Tutorial

Wordscores is a scaling model for estimating the positions (mostly of political actors) for dimensions that are specified a priori. Wordscores was introduced in Laver, Benoit and Garry (2003) and is widely used among political scientists.

```{r eval = T}
library(quanteda)
library(quanteda.textmodels)
library(quanteda.corpora) # Die Anleitung zur Installierung findet ihr hier: https://github.com/quanteda/quanteda.corpora
library(quanteda.textplots) # Für mehr Infos siehe: https://quanteda.io/articles/pkgdown/examples/plotting.html
```

Training a Wordscores model requires reference scores for texts whose policy positions on well-defined a priori dimensions are “known”. Afterwards, Wordscores estimates the positions for the remaining “virgin” texts.

We use manifestos of the 2013 and 2017 German federal elections. For the 2013 elections we assign the average expert evaluations from the 2014 [Chapel Hill Expert Survey](https://www.chesdata.eu/) for the five major parties, and predict the party positions for the 2017 manifestos.

```{r eval = T}
corp_ger <- download(url = "https://www.dropbox.com/s/uysdoep4unfz3zp/data_corpus_germanifestos.rds?dl=1")
summary(corp_ger)
```

Now we can apply the Wordscores algorithm to a document-feature matrix.

```{r eval = T}
# create a document-feature matrix
dfmat_ger <- dfm(corp_ger, remove = stopwords("de"), remove_punct = TRUE)

# apply Wordscores algorithm to document-feature matrix
tmod_ws <- textmodel_wordscores(dfmat_ger, y = corp_ger$ref_score, smooth = 1)
summary(tmod_ws)
```

Next, we predict the Wordscores for the unknown virgin texts.

```{r eval = T}
pred_ws <- predict(tmod_ws, se.fit = TRUE, newdata = dfmat_ger)
```

Finally, we can plot the fitted scaling model using quanteda‘s `textplot_scale1d` function.

```{r eval = T}
textplot_scale1d(pred_ws)
```